PRS dendrogram clusters

### 2021-02-22 notebooks/17-PRS_dendrogram_cluster_investigation-020921.Rmd
fixed effector/sensor coloring of clusters

```{r}
library(reticulate)
source('src/R/get.subclusters.dendrogram.R')
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('src/R/plot_density_prs.R')
library(RColorBrewer)
col = brewer.pal(n=9,name='Set1')
sensor_colors = col[1:6]
effector_colors = col[7:9]
```

@@

sensors_pcc = e_pcc.sensors_df#e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
effector_pcc = e_pcc.effectors_df
sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
effector_order = effector_pcc.groupby('go_group').eff.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_group').sens.median().sort_values().index.tolist()
effector_colors_dict = dict(zip(effector_order,r.effector_colors))
sensor_colors_dict = dict(zip(sensor_order,r.sensor_colors))
#sensor_colors_dict['none']=sensor_colors_dict[None]
#del sensor_colors_dict[None]
```

@@

```
# Plot heatmap
Using the clustering with `euclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis

@@

go_color_map = unlist(append(py$effector_colors_dict,py$sensor_colors_dict))
go_color_map['none'] = 'white'
clrs = map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()

rowColors = rowAnnotation(rowColors=clrs,
                          col=list(rowColors = go_color_map ),
                          #width=unit(100,'mm'),
                          simple_anno_size=unit(3,'cm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
colColors = columnAnnotation(colColors=clrs,
                          col=list(colColors = go_color_map ),
                          simple_anno_size=unit(3,'cm'),
                          #annotation_height=unit(20,'mm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
rowAnnot = HeatmapAnnotation(Effectiveness=anno_lines(rowSums(py$prs_mat)),
                            which='row',
                            name='Effectiveness', 
                            gp = gpar(col='blue'),
                            annotation_name_side = 'top',
                            annotation_name_rot= 0,
                            border=FALSE,
                          show_legend=FALSE
)
colAnnot = HeatmapAnnotation(Sensitivity=anno_lines(colSums(py$prs_mat)), 
                             which='col', 
                             name='Sensitivity',
                            gp = gpar(col='blue'),
                            annotation_name_side = 'left',
                            annotation_name_rot=0,
                            border=FALSE,
                          show_legend=FALSE
)
pdf('tmp_heatmap.pdf')
Heatmap(py$prs_mat_cl, 
        cluster_rows = as.dendrogram(hclust_row),
        cluster_columns=as.dendrogram(hclust_col),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
        row_dend_width = unit(20,'mm'),
        column_dend_height = unit(20,'mm'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()

>>>>

```{r}
library(reticulate)
#use_python("/home/oma21/miniconda3/envs/enm/bin/python")
use_condaenv('enm')
setwd('../')
#source('src/R/plot_density_prs.R')
source('src/R/get.subclusters.dendrogram.R')
library(RColorBrewer)
col = colorRampPalette(brewer.pal(n=9,name='Set1'))(10)
sensor_colors = col[1:8]
effector_colors = col[9:10]
```

@@

sensors_pcc = e_pcc.sensors_df#e_pcc.df.loc[e_pcc.df.sens>np.quantile(e_pcc.df.sens,0.99)]
effector_pcc = e_pcc.effectors_df
sensor_sub_pcc = get_subnetwork(e_pcc.graph_gc, sensors_pcc.orf_name.values)
effector_sub_pcc = get_subnetwork(e_pcc.graph_gc, effector_pcc.orf_name.values)
effector_order = effector_pcc.groupby('go_term').eff.median().sort_values().index.tolist()
sensor_order = sensors_pcc.groupby('go_term').sens.median().sort_values().index.tolist()
effector_colors_dict = dict(zip(effector_order,r.effector_colors))
sensor_colors_dict = dict(zip(sensor_order,r.sensor_colors))
#sensor_colors_dict['none']=sensor_colors_dict[None]
#del sensor_colors_dict[None]
```

@@

```
# Plot heatmap
Using the clustering with `seuclidian` distance and `ward` linkage, plot the heatmap with row and column colors are the GO term annotations found from effector and sensor analysis

@@

go_color_map = unlist(append(py$effector_colors_dict,py$sensor_colors_dict))
go_color_map['none'] = 'white'
clrs = go_color_map# map(py$eff_sens_go_list, ~ifelse(is.null(.x), 'none',.x))%>%unlist()

rowColors = rowAnnotation(rowColors=py$e_pcc$df%>%left_join(py$effector_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.na(.x), 'none',.x))%>%unlist(),
                          col=list(rowColors = go_color_map ),
                          #width=unit(100,'mm'),
                          simple_anno_size=unit(3,'cm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
colColors = columnAnnotation(colColors=py$e_pcc$df%>%left_join(py$sensors_pcc)%>%select(go_term)%>%pull%>%map(~ifelse(is.null(.x), 'none',
                                                                                                                      ifelse(is.nan(.x),'none',.x)))%>%unlist(),
                          col=list(colColors = go_color_map ),
                          simple_anno_size=unit(3,'cm'),
                          #annotation_height=unit(20,'mm'),
                          show_annotation_name=FALSE,
                          show_legend=FALSE)
rowAnnot = HeatmapAnnotation(Effectiveness=anno_lines(rowSums(py$prs_mat)),
                            which='row',
                            name='Effectiveness', 
                            gp = gpar(col='blue'),
                            annotation_name_side = 'top',
                            annotation_name_rot= 0,
                            border=FALSE,
                          show_legend=FALSE
)
colAnnot = HeatmapAnnotation(Sensitivity=anno_lines(colSums(py$prs_mat)), 
                             which='col', 
                             name='Sensitivity',
                            gp = gpar(col='blue'),
                            annotation_name_side = 'left',
                            annotation_name_rot=0,
                            border=FALSE,
                          show_legend=FALSE
)
pdf('tmp_heatmap.pdf')
Heatmap(py$prs_mat_cl, 
        cluster_rows = as.dendrogram(hclust_row),
        cluster_columns=as.dendrogram(hclust_col),
        col=RColorBrewer::brewer.pal(9,'YlGnBu'),
        row_dend_width = unit(20,'mm'),
        column_dend_height = unit(20,'mm'),
        right_annotation=rowAnnot,
        left_annotation = rowColors,
        bottom_annotation=colAnnot,
        top_annotation=colColors,
        show_heatmap_legend=TRUE
)
dev.off()
